Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Revised and rewriting conclusions, closes #21, and thank you everyone, good night

This work introduces a self-adaptive user-centric end-to-end system, named MUSES. The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system. %Antares - Yo podrían en lugar de ``next year'' el año, porque el artículo puede ser leído en cualquier momento y es mejor emplear referencias absolutas, ¿no creeis? FERGU: fuera

@@

In addition, a scientific comparison between the techniques used in the presented system and those in the literature, in the same scope, has been done.

We can conclude that MUSES offers several advantages over the existing tools, both the some of its `technical' features, but also in the application of Data Mining, Machine Learning and Computational Intelligence methods to the events gathered by the system (users' behaviour), in order to adapt or refine the set of security rules.

Anyway, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.

>>>>

This work introduces a self-adaptive user-centric end-to-end system, named MUSES. The first prototype of this system has been recently released, and it has been already tested in an actual company. The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system. %Antares - Yo podrían en lugar de ``next year'' el año, porque el artículo puede ser leído en cualquier momento y es mejor emplear referencias absolutas, ¿no creeis? FERGU: fuera

@@

In addition, a scientific comparison between the techniques used in the presented system and those in the literature, in the same scope, has been done. It has been discussed that MUSES has the advantage of being multiplatform, while most of the reviewed tools are not. In addition, MUSES is able to adapt and evolve the security policies that a company has built, and not only apply them, as the other tools do. Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the aim of going beyond the state of the art in different fields of research.

However, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES. The second prototype of the system will be also released, as well as the conclusions extracted after the analysis of data from the test of the first prototype.
